Large squeezing in multicomponent trapped Bose-Einstein condensates

### 2012-12-17 large_number_squeezing_with_atoms.tex
Minor work on Bog section

\section{Squeezing in 2D and 3D}
The simulations in the previous two sections were one dimensional, and show how having spatially constant density and using a $\pi$-pulse will improve the resultant squeezing.  While these conclusions remain valid for simulations in two or three dimensions, adding each additional dimension results in a degradation of the squeezing.  This is true even when the potential (and the resulting atomic density) is constant across the bulk of the trap.  Furthermore, the expected squeezing goes down as the volume of the trap increases.  This can be seen in Fig.~\ref{figDimensionalSqueezingEffects}, where we show the squeezing generated in 1D, 2D and 3D BECs for two different parameter regimes. In both cases we take the BEC to be trapped in a box potential, which in the Thomas-Fermi limit leads to a constant density profile across the BEC. In Figure~\ref{figDimensionalSqueezingEffects}a we consider the case where $U_{aa}=U_{bb}\neq 0$, $U_{ab}=0$, while in Figure~\ref{figDimensionalSqueezingEffects}b we consider the case $U_{aa}\neq 0$, $U_{ab}=U_{bb}=0$. In both cases it is clear that number squeezing is best in lower dimensions, and becomes degraded or non-existent as we move to a three dimensional system; the effect is worse if more than one nonlinearity is non-zero.

@@

>>>>

\section{Squeezing in 2D and 3D}

The simulations in the previous two sections were one dimensional, and show how having spatially constant density and using a $\pi$-pulse will improve the resultant squeezing.  While these conclusions remain valid for simulations in two or three dimensions, adding each additional dimension results in a degradation of the squeezing.  This is true even when the potential (and the resulting atomic density) is constant across the bulk of the trap.  Furthermore, the expected squeezing goes down as the volume of the trap increases.  This can be seen in Fig.~\ref{figDimensionalSqueezingEffects}, where we show the squeezing generated in 1D, 2D and 3D BECs for two different parameter regimes. In both cases we take the BEC to be trapped in a box potential, which in the Thomas-Fermi limit leads to a constant density profile across the BEC. In Figure~\ref{figDimensionalSqueezingEffects}a we consider the case where $U_{aa}=U_{bb}\neq 0$, $U_{ab}=0$, while in Figure~\ref{figDimensionalSqueezingEffects}b we consider the case $U_{aa}\neq 0$, $U_{ab}=U_{bb}=0$. In both cases it is clear that number squeezing is best in lower dimensions, and becomes degraded or non-existent as we move to a three dimensional system; the effect is worse if more than one nonlinearity is non-zero.

@@

To minimise the damaging effects of the non-zero momentum modes, it is better to operate in a regime where the total occupation of the non-zero momentum modes $N_{\mathbf{k}\neq 0}$ is small.
